### 2018-05-16 Sections/economics_of_the_quantum_internet.tex
Minor quantcoin graphics update
minor

What if we were to replace brute-force hashing of random data with computations of genuine monetary value? Then we would have a sounder currency, whose value derives from the monetary cost of executing computations. While it is not so easy to invent such a protocol for classical computation, the idea lends itself very naturally to quantum computation, owing to their ability to undergo encrypted computation and be subject to verification protocols.

In Alg.~\ref{alg:quant_coin} we provide a very rough sketch for how such a protocol might be constructed. We do so in a very high-level manner, abstracting away the implementation details of the computation, encryption, and verification protocols.

@@

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{quantcoin_protocol}
\caption{\comment{To do}}\label{fig:quantcoin_protocol}	
\end{figure}

@@

Note that we observe an expansion in the money supply with each successfully executed and verified computation. There is no inherent theoretical upper limit on the number of coins that can exist. However the QuantCoin\texttrademark\, money supply will be limited for the practical reason that mining each one is associated with a monetary transaction between Alice and Bob, and Alice will eventually run out of assets to exchange for computations.

@@

Alternately, rather than Alice paying Bob's reward in dollars, she might pay for them in already-existing QuantCoins. Suppose Alice pays $\lambda$ QuantCoins\texttrademark\, as Bob's reward. Then Eq.~(\ref{eq:value_quantcoins}) reduces to,
\begin{align}
&(\text{Dollar value of a QuantCoin\texttrademark\,)}\\
&=\frac{1}{\lambda}(\text{Dollar value of cost of execution for Bob}),\nonumber
\end{align}
providing us with a simple financial model relating the market price of QuantCoins\texttrademark\, and the monetary cost of execution of computations.

Note that with exception to the scenario where Alice buys into QuantCoins\texttrademark\, using dollar currency, the entire protocol is self-enforcing via Blockchain transactions. Bob doesn't get paid his newly earned and freshly printed QuantCoin\texttrademark\, until the verification of the computation has completed and the proof committed to the Blockchain. He therefore cannot get paid until he has executed the computation he promised to, and proven to the network that he actually did.

@@

However, if the upfront payment were being made in pre-existing QuantCoins\texttrademark\,, the Blockchain might be programmed to not release the reward until completion of the final verification stage of the protocol -- effectively an escrow programmed directly into the Blockchain for execution.

As described above, the cryptocurrency is effectively backed by the spot market in computation -- we exchange currency for the execution of computations \textit{immediately}. However, one might also envisage more complex cryptocurrencies being backed by the futures market in the licensing of quantum compute-time. Intuitively, one would expect such a form of cryptocurrency to be sounder than the one backed by the spot market. This is because our spot market-derived coins, once mined are not guaranteed to be convertible to anything of value, including computations. Recall that the execution of the computation takes place immediately when the coin is created. On the other hand, a QuantCoin\texttrademark\, backed by a guarantee to access quantum compute-time at a designated point in the future necessarily has value, so long as the demand for compute-time does, and maintains value until the contract matures and converts into compute-time at which point it becomes worthless.

>>>>

What if we were to replace brute-force hashing of random data with computations of genuine monetary value? Then we would have a sounder currency, whose value derives from the monetary cost of executing useful computations. While it is not so easy to invent such a protocol for classical computation, the idea lends itself very naturally to quantum computation, owing to their ability to undergo encrypted computation and be subject to verification protocols.

Building upon some of the pricing models introduced earlier in this section, there are two main candidates for backing a cryptocurrency with quantum compute-time: the spot market (i.e we execute the computation immediately); and the futures market (i.e we own the right to utilise the computer at some fixed time in the future). We consider the merits of both these candidates.

%
% Spot Market Model
%

\subsubsection{Spot market model}\index{Spot market}

In Alg.~\ref{alg:quant_coin} we provide a very rough sketch for how a protocol based on the spot market might be constructed. A corresponding graphical flowchart is shown in Fig.~\ref{fig:quantcoin_protocol}. We the ideas in a very high-level manner, abstracting away the implementation details of the computation, encryption, and verification protocols, instead envisaging that we can interface with them using a very high-level API\index{API}.

@@

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{quantcoin_protocol}
\caption{Flowchart for the QuantCoin\texttrademark\, protocol, introduced in Alg.~\ref{alg:quant_coin}.}\label{fig:quantcoin_protocol}	
\end{figure}

@@

Note that we observe an expansion in the money supply with each successfully executed and verified computation -- one additional unit of QuantCoins\texttrademark\, is mined for every unit of computation implemented. Unlike Bitcoin, there is no inherent theoretical upper limit on the number of coins that can exist. However the QuantCoin\texttrademark\, money supply\index{Money supply} will be limited for the practical reason that mining each one is associated with a monetary transaction between Alice and Bob, and Alice will eventually run out of assets to exchange for computations.

@@

Alternately, rather than Alice paying Bob's reward in dollars, she might pay for them in already-existing QuantCoins\texttrademark. Suppose Alice pays $\lambda$ QuantCoins\texttrademark\, as Bob's reward. Then Eq.~(\ref{eq:value_quantcoins}) reduces to,
\begin{align}
&(\text{Dollar value of a QuantCoin\texttrademark\,)}\\
&=\frac{1}{\lambda}(\text{Dollar value of cost of execution for Bob}),\nonumber
\end{align}
providing us with a simple financial model relating the market price of QuantCoins\texttrademark\, and the monetary cost of execution of computations.

Note that with exception to the scenario where Alice buys into QuantCoins\texttrademark\, using dollar currency (or any non-electronic asset that cannot be committed to the Blockchain), the entire protocol is self-enforcing via Blockchain transactions. Bob doesn't get paid his newly earned and freshly printed QuantCoin\texttrademark\, until the verification of the computation has completed and the proof committed to the Blockchain. He therefore cannot get paid until he has executed the computation he promised to, and proven to the network that he actually did.

@@

However, if the upfront payment were being made in pre-existing QuantCoins\texttrademark\,, the Blockchain might be programmed to not release the reward until completion of the final verification stage of the protocol -- effectively an escrow programmed directly into the Blockchain for self-execution.

%
% Futures Market Model
%

\subsubsection{Futures market model}

As described above, the cryptocurrency is effectively backed by the spot market in computation -- we exchange currency for the execution of computations \textit{immediately}. However, one might also envisage more complex cryptocurrencies being backed by the futures market in the licensing of quantum compute-time.

Intuitively, one would expect such a form of cryptocurrency to be sounder than the one backed by the spot market. This is because our spot market-derived coins, once mined are not guaranteed to be convertible to anything of value, including computations. Recall that the execution of the computation takes place immediately when the coin is created.

On the other hand, a QuantCoin\texttrademark\, backed by a guarantee to access quantum compute-time at a designated point in the future necessarily has value, so long as the demand for compute-time does, and maintains value until the contract matures and converts into compute-time at which point it becomes worthless.
